ACNP 2024 MS ANXIETY

### 2024-08-09 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
Add files via upload

>>>>

#figure brainstorming
1. Flowchart of inclusion/exclusion
2. Demographics (age, sex, race, +/- PHQ2, PHQ9, has anxiety dx, on anxiety meds, both, on dmt) 
3. Some sort of schematic of pipeline - 
  a. amygdala - mpfc blobs
  b. uncinate connecting the two
  c. white matter lesion dropped in uncinates
  d. streamline filtering
  e. mean of both side
4. Mean UF Anxiety diagnosis either violin or bar
5. Mean Anxiety dose either violin or bar
6. Supplement: 
 - More detailed streamline filtering
 - Depression group uncinate burden
 - Fornix diagnosis and dose; depression group
